### 2021-03-12 manuscript/supplementary.tex
Major revision for manuscript and figures after comments from Mik.

\PaperTitle{Supplementary results for: A meta-analysis of bioinformatics software benchmarks reveals that publication-bias unduly influences software accuracy} % Article title

@@

\begin{figure}[H]
\centering
\includegraphics[height=0.7\textheight]{litMiningFlowDiagram-edited.pdf}
\caption{In order to improve the identification of benchmark articles
  that rank both accuracy and speed we developed a tool for ranking
  PubMed articles based upon word association scores (measured in
  ‘bits’). In brief, keywords were extracted from titles and abstracts
  for both training (in this case benchmark articles) and background
  articles (articles published between 2013 and 2015 with
  “bioinformatics” in the title or abstract). Log-odds ratios were
  computed for each keyword (measured in ‘bits’). Candidate articles
  that matched a hand-selected list of keywords associated with
  benchmarks were then scored and ranked with a “sum of bits”
  score. High ranking articles were then inspected, those that met our
  criteria were added to the training set, those that didn’t were
  added to the background set of articles.}
\label{fig:flow}
\end{figure}

\begin{figure}[H] \centering
\includegraphics[width=1.05\textwidth]{wordScores.pdf} \caption{The 40
  highest and lowest scoring words that are associated with
  bioinformatic benchmark articles from the training benchmark articles,
  compared to the background articles. The log-odds ratios (measured
  in bits) are indicated on the y-axis. }
\label{fig:wordScores} \end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-small.pdf}
\caption{The distributions for the measures we expected to be
  predictive of software quality used in this study. These
are, reading from left to right, top to bottom: Accuracy -- the mean
normalised accuracy rank for each benchmarked method; Speed -- the
mean normalised speed rank for each benchmarked method;
JH5 -- the Journal H5 index to the highest impact journal that has published
a manuscript describing a method, data from GoogleScholar 2020 Metrics;
Cites -- the number of citations to the most cited manuscript describing a method, data from GoogleScholar;
H-index -- the H-index for the highest profile corresponding author from the
manuscripts describing a method, data from GoogleScholar User Profiles;
M-index -- the M-index (H-index/(\#years since first publication)) for the
highest profile corresponding author from the manuscripts describing a method,
data from GoogleScholar User Profiles;
Relative ages for different tools, for each benchmark tools were ranked based upon publication dates, these ranks were normalised to lie between 0 and 1.
}
\label{fig:metricDistributions}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{hindex-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{cites-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Citation metrics and software tool speeds/accuracies.} Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $10 \times
  10$ matrix. The shading indicates different median citation-based
  feature scores (redder shade indicates a higher value).  The shading
  indicate median H-indices ({\bf left}) and $log_{10}(citations)$
  ({\bf right}). }
\label{fig:heatmaps}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{commits-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{contributors-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Version control use and software tool speeds/accuracies.}
  Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $10 \times
  10$ matrix. The shading indicates different median github-derived
  feature scores (redder shade indicates a higher value).  The shading
  indicate the number of commits ({\bf left}) and the number of code contributors
  ({\bf right}).
 }
\label{fig:heatmapsCommits}
\end{figure}

>>>>

\PaperTitle{Supplementary results for: A meta-analysis of bioinformatics software benchmarks reveals major influences on software accuracy} % Article title

@@

\begin{figure}[H]
\centering
\includegraphics[height=0.7\textheight]{litMiningFlowDiagram-edited.pdf}
\caption{In order to improve the identification of benchmark articles
  that rank both accuracy and speed we developed a tool for ranking
  PubMed articles based upon word association scores (measured in
  ‘bits’). In brief, keywords were extracted from titles and abstracts
  for both training (in this case benchmark articles) and background
  articles (articles published between 2013 and 2015 with
  “bioinformatics” in the title or abstract). Log-odds ratios were
  computed for each keyword (measured in ‘bits’). Candidate articles
  that matched a hand-selected list of keywords associated with
  benchmarks: \texttt{((bioinformatics OR (computational AND biology)) AND (algorithmic OR algorithms OR biotechnologies OR computational OR kernel OR methods OR procedure OR programs OR software OR technologies)) AND (accuracy OR analysis OR assessment OR benchmark OR benchmarking OR biases OR comparing OR comparison OR comparisons OR comparative OR comprehensive OR effectiveness OR estimation OR evaluation OR metrics OR efficiency OR performance OR perspective OR quality OR rated OR robust OR strengths OR suitable OR suitability OR superior OR survey OR weaknesses OR correctness OR correct OR evaluate OR competing OR competition) AND (complexity OR cputime OR runtime OR walltime OR duration OR elapsed OR fast OR faster OR perform OR performance OR slow OR slower OR speed OR time OR (computational AND resources))}. These 
  were then scored and ranked with a “sum of bits”
  score. High ranking articles were then inspected, those that met our
  criteria were added to the training set, those that did not were
  added to the background set of articles.}
\label{fig:flow}
\end{figure}

\begin{figure}[H] \centering
\includegraphics[width=0.99\textwidth]{wordScores.pdf} \caption{The 40
  highest and lowest scoring words that are associated with
  bioinformatic benchmark articles from the training benchmark articles,
  compared to the background articles. The log-odds ratios (measured
  in bits) are indicated on the y-axis. }
\label{fig:wordScores} \end{figure}

@@

\begin{figure}[htb!]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-small.pdf}
\caption{The distributions for the measures we expected to be
  predictive of software quality used in this study. These
are, reading from left to right, top to bottom: Accuracy -- the mean
normalised accuracy rank for each benchmarked method; Speed -- the
mean normalised speed rank for each benchmarked method;
JH5 -- the Journal H5 index to the highest impact journal that has published
a manuscript describing a method, data from GoogleScholar 2020 Metrics;
Cites -- the number of citations to the most cited manuscript describing a method, data from GoogleScholar;
H-index -- the H-index for the highest profile corresponding author from the
manuscripts describing a method, data from GoogleScholar User Profiles;
M-index -- the M-index (H-index/(\#years since first publication)) for the
highest profile corresponding author from the manuscripts describing a method,
data from GoogleScholar User Profiles;
Relative ages for different tools, for each benchmark tools were ranked based upon publication dates, these ranks were normalised to lie between 0 and 1.
}
\label{fig:metricDistributions}
\end{figure}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-distributions-permuted.pdf}
\caption{The distributions for the permuted accuracy and speed values, where accuracy and speed ranks have been normalised to lie between 0 and 1.
}
\label{fig:metricDistributionsPerm}
\end{figure}

\clearpage

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{hindex-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{cites-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Citation metrics and software tool speeds/accuracies.} Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $3 \times
  3$ matrix. The shading indicates different median citation-based
  feature scores (redder shade indicates a higher value).  The shading
  indicate median H-indices ({\bf left}) and $log_{10}(citations)$
  ({\bf right}). }
\label{fig:heatmaps}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{commits-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{contributors-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Version control use and software tool speeds/accuracies.}
  Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $3 \times
  3$ matrix. The shading indicates different median github-derived
  feature scores (redder shade indicates a higher value).  The shading
  indicate the number of commits ({\bf left}) and the number of code contributors
  ({\bf right}).
 }
\label{fig:heatmapsCommits}
\end{figure}
